### 2019-09-19 README.Rmd
updated example in readme

>>>>

- Should I write the code in a package or just save the functions in a folder in the paper repository?
- Sometimes LIME does not want to run in R with the bullet data

```{r error = TRUE, message = FALSE}
library(lime)

# Split up the data set
iris_test <- iris[1:5, 1:4]
iris_train <- iris[-(1:5), 1:4]
iris_lab <- iris[[5]][-(1:5)]

# Create Random Forest model on iris data
#model <- caret::train(iris_train, iris_lab, method = 'rf')
model <- randomForest::randomForest(iris_train, iris_lab)

# Create an explainer object
explainer <- lime(iris_train, as_classifier(model))

# Explain new observation
explanation <- explain(iris_test, explainer, n_labels = 1, n_features = 2)
```
